---
title: "HW MARKDOWN"
author: "Cara"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#first we'll load our libraries
```{r}
library(tidyverse)
library(lubridate)
library(dplyr)
```

# run this to load the data for this assignment
# it will create a dataframe called "impeach," with all House Democrats

```{r}
impeach <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRh8d5JaDqBtByzNw2JZF3idaACobDhhk-p7chJoktA0HawELHFOvjQOqCpzGA4MGONvPlR7GASqW-K/pub?gid=1765341510&single=true&output=csv")

view(impeach)
```

FOR EACH OF THE QUESTIONS BELOW, WRITE YOUR WORKING R CODE TO RETURN THE REQUESTED RESULTS
USE COMMENTS (PREFACED BY THE #) BEFORE THE WORKING CODE TO EXPLAIN WHAT YOU'RE DOING FOR EACH STEP

1) The column "for_impeachment" indicates whether the member has publicly called for an impeachment inquiry. Filter to return only the ones where the answer is NO.    

For this question, I filtered for only the NO responses in the for_impeachment column. 

```{r}
impeach %>% filter(for_impeachment=="NO")
```

2) Filter to return only results where a member is both against impeachment, and comes from a district that President Trump won in 2016 (which is noted in the "p16winningparty" column)

I filtered for NO in for_impeachment and R in p16winningparty.
```{r}
impeach %>% filter(for_impeachment=="NO", p16winningparty=="R")
```
3) Filter for only results where a member is against impeachment, comes from a district that President Trump won in 2016 (which is noted in the "p16winningparty" column),and also comes from a district that Mitt Romney won in 2012 ("p12winningparty").

I filtered for NO in for_impeachment, R in p16winningparty, and R in p12winningparty.

```{r}
impeach %>% filter(for_impeachment=="NO", p16winningparty=="R",  p12winningparty=="R")
```


4) Filter for only results from September 2019 where a member is a YES for impeachment. 

I filtered for YES in the for_impeachment column, 9 (September) in the date_month column, and 2019 in the date_year column. 

```{r}
impeach %>% filter (for_impeachment=="YES", date_month=="9", date_year=="2019") 
```

4) Filter for only results where a member is a YES for impeachment and is from a district where Clinton won more than 70 percent of the vote in 2016 (found in column "clinton_percent")

I filtered for YES in the for_impeachment column and over (>) 70 in the clinton_percent column. 

```{r}
impeach %>% filter (for_impeachment=="YES", clinton_percent>"70") 
```

5) Sort the entire dataframe based on the percentage of a district that has a bachelor's degree or higher ("pct_bachelors"), from lowest to highest

I used the order function on the column pct_bachelors to sort the dataframe from lowest to highest.

```{r}
impeach[order(impeach$pct_bachelors),]
```

6) Sort the just those who are NO on impeachment based on the percentage of a district that has a bachelor's degree or higher ("pct_bachelors"), from lowest to highest

For this problem, I first created a new dataset that just includes those that responded NO to impeachment. I saved that dataset under the name no_impeach. Then I fused the order funtion to sort no_impeach from lowest to highest.

```{r}
no_impeach <- impeach %>% filter(for_impeachment=="NO")
view(no_impeach)

no_impeach[order(no_impeach$pct_bachelors),]

```
 
 7) Sort the just those who are NO on impeachment based on the percentage of a district that has a  bachelor's degree or higher ("pct_bachelors"), from lowest to highest. Then filter those records by only those whose bachelor's percentage is below the national average (found in the "pct_bachelors_compared_to_national" column).

```{r}
no_impeach[order(no_impeach$pct_bachelors),] %>% filter (pct_bachelors_compared_to_national=="BELOW")
```

8) Filter for only members from New Jersey who are NO on impeachment

```{r}
impeach %>% filter (state=="NJ", for_impeachment=="NO") 
```
  


9) Filter for those who were YES on impeachment, with a declared date prior to 2019. So only those with dates before 2019.  Then sort those so that the highest Clinton vote percentages are 
at the top.  


```{r}

impeach[order(-impeach$clinton_percent),] %>% filter(for_impeachment=="YES", date_year<"2019")

```

 10) Answer this question with a single numeric answer, and show the R code you used to reach that answer: How many members in the dataset who are holdouts (NO) on impeachment comes from districts with a GDP below the national figure?
 
 = 19
 

```{r}

count(impeach %>% filter(for_impeachment=="NO", gdp_above_national=="BELOW"))
```








